How to Write Theses\\ With Two Line Titles

### 2020-04-13 chapters/methodology/collection.tex
final draft

\section{Tools}
\subsection{Jupyter}
The Jupyter Notebook is an open-source web application that supports data cleaning and transformation, numerical simulation, statistical modeling, data visualization, machine learning, etc. by allowing us to create and share documents that contain live code, equations, visualizations and narrative text. Jupyter allows for displaying the result of computation inline in the form of rich media (SVG, LaTeX, etc.). The Jupyter notebook combines two components:
\begin{itemize}
  \item \textbf{A web application}: a browser-based tool for interactive authoring of documents which combine explanatory text, mathematics, computations and their rich media output.
  \item \textbf{Notebook documents}: a representation of all content visible in the web application, including inputs and outputs of the computations, explanatory text, mathematics, images, and rich media representations of objects.
\end{itemize}
Jupyter notebook is gaining rapid popularity in the field of data science for making sharing documentation and codes for replication very easy. In this project, the codes are written in python notebook which can be accessed from http://github.com/.

\subsection{Tensorflow}
TensorFlow\textsuperscript{TM} is an open source software library developed within Google’s AI organization by the Google Brain team with a strong support for machine learning and deep learning. Its flexible architecture allows easy deployment of computation across a variety of platforms (CPUs, GPUs, TPUs), and from desktops to clusters of servers to mobile and edge devices. It is being used at a number of well known companies like Uber, Google, AMD, etc. for high performance numerical computation and machine learning. While TensorFlow is capable of handling a wide range of tasks, it is mainly designed for deep neural network models. It will serve as baseline to test the metamorphic relations identified in section \ref{MRused}.

\section{Algorithm}
\subsection{Convolutional neural network}
\subsection{2-layer neural network}

\section{Dataset}
\subsection{MNIST Dataset}
The MNIST database of handwritten digits maintained by Yann LeCun \cite{MNIST}, has a training set of 55,000 examples, and a test set of 10,000 examples. It is a subset of a larger set available from NIST. The digits have been size-normalized and centered in a fixed-size image. It is a good database for people who want to try learning techniques and pattern recognition methods on real-world data while spending minimal efforts on preprocessing and formatting. The MNIST database was constructed from NIST's Special Database 3 and Special Database 1 which contain binary images of handwritten digits. The original black and white (bilevel) images from NIST were size normalized to fit in a 20x20 pixel box while preserving their aspect ratio. The images were centered in a 28x28 image by computing the center of mass of the pixels, and translating the image so as to position this point at the center of the 28x28 field.

@@

\begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/digit.png}
            \caption{Sample EMNIST-MNIST dataset}
            \label{fig:EMNIST MNIST dataset}
        \end{subfigure}%
        \label{fig:Rotate-misclassifications}
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/letter.png}
            \caption{Sample EMNIST-MNIST dataset}
            \label{fig:EMNIST MNIST dataset}
        \end{subfigure}%
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Fashion MNIST Dataset}
Fashion-MNIST is a dataset of Zalando's article images—consisting of a training set of 55,000 examples and a test set of 10,000 examples. Each example is a 28x28 grayscale image, associated with a label from 10 classes.

>>>>

 \section{Tools}
We used Python as the programming language to implement our code. We chose Python because of it's popularity and easy syntax. There are also a plenty of Pythonn libraries like Tensorflow, Keras and scikit-learn available to easily implement machine learning, deep-learning, natural language processing algorithms. Along with Python as a programming language we also used following programs, tools, and datasets to perform our experiment.
\subsection{HCC}
Due to the high computation requirements for some dataset we needed a faster and reliable hardware. The Holland Computing Center (HCC) claim to be the fastest resource in the state of Nebraska. HCC provides these services to researcher and students associated with any campus of the University of Nebraska system. Some shared services are available for free and dedicated services can be obtained for a modest price. We used their servers to run our Jupyter notebooks.

\subsection{Jupyter Notebook}
Jupyter notebook is part of project Jupyter which aims to provide interactive interface for development across multiple platforms and programming languages. Jupyter's web interface supports data cleaning, data transformation and visualization, numerical operations etc. It allows us to create live code snippets and equations and shows results of inline computation right next to the code in the form of rich media (SVG, LaTeX etc). It combines two components: 
\begin{itemize}
  \item \textbf{A web application}: a web-based interactive tool to write code, markdown, etc. It also displays the rich media output.
  \item \textbf{Notebook documents}: a representation of all the content written and displayed using the web application.
\end{itemize}
Jupyter notebook is gaining rapid popularity in the field of data science for making sharing documentation and codes for replication very easy. In this project, the codes are written in python notebook which can be accessed from our github repository.

\subsection{Tensorflow}
TensorFlow is an end-to-end open source platform for machine learning. It has a comprehensive, flexible ecosystem of tools, libraries and community resources that lets researchers push the state-of-the-art in ML and developers easily build and deploy ML powered applications
TensorFlow\textsuperscript{TM} is an open source software library developed within Google’s AI organization by the Google Brain team with a strong support for machine learning and deep learning. Its flexible architecture allows easy deployment of computation across a variety of platforms (CPUs, GPUs, TPUs), and from desktops to clusters of servers to mobile and edge devices. It is being used at a number of well known companies like Uber, Google, AMD, etc. for high performance numerical computation and machine learning. While TensorFlow is capable of handling a wide range of tasks, it is mainly designed for deep neural network models. It will serve as baseline to test the metamorphic relations identified in section \ref{MRused}. Tensorflow provides api for loading the MNIST dataset identified in section \ref{dataset}. We also used tensorflow to implement neural network and convolutional neural network defined in section \ref{Algorithms}

\subsection{Scikit-learn}
Scikit-learn is a Python module for machine learning built on top of SciPy and is distributed under the 3-Clause BSD license.
It provides a range of supervised and unsupervised learning algorithms via a consistent interface in Python.

\section{Algorithms}\label{Algorithms}
We implemented some popular machine learning algorithms to test our hypothesis that "small changes to input data will not affect the accuracy of the model drastically". We used TensorFlow and scikit-learn to implement the machine learning algorithms. 
\subsection{Convolutional neural network}
The images in the MNIST dataset is a one dimensional vector of 784 features (28x28 pixels). We first reshape the images to match the picture format height x width x channel. Each image in the MNIST dataset is now a single-channel of 28x28x1 size. The images are now fed into the network as input. The first convolution layer has 32 filters with a kernel size of five. The activation function we used is the ReLU function and the output from this layer is fed into a pooling layer. The data goes through another iteration of convolution and pooling before being flattened and sent to the fully connected layer. The output layer gives us a number which corresponds to the class of the image it is assigned to.

\subsection{Neural network}

 Hidden fully connected layer with 256 neurons. Each hidden layer is made up of a set of neurons, where each neuron is fully connected to all neurons in the previous layer, and where neurons in a single layer function completely independently and do not share any connections. If the image is a 64 by 64 greyscale image, then we'd have 64x64=4,096 input neurons, with the intensities scaled appropriately between 0 and 1. The output layer will contain just a single neuron, with output values of less than 0.5 indicating "input image is not a 9", and values greater than 0.5 indicating "input image is a 9 ". The input pixels are greyscale, with a value of 0.0 representing white, a value of 1.0 representing black, and in between values representing gradually darkening shades of grey. The second layer of the network is a hidden layer.

2 layer

\subsection{Naive Bayes}
We used scikit-learn to implement Naive Bayes algorithm. The images were first transformed to a one dimensional vector of 784 features. 
A naive bayes classifier is then created using the $sklearn.naive\_bayes.MultinomialNB()$ function. This classifier is then fitted using the $fit()$ function, which takes the images and labels as input and fits the classifier according to the images and labels. The resulting classifier is then used to predict the labels of test data.

\subsection{$k$-Nearest Neighbor}
 We used scikit-learn to implement our $k$-nearest neighbor algorithm. Scikit's $sklearn.neighbors$ module provides functionality for unsupervised and supervised neighbors-based learning methods. 
 The $KNeighborsClassifier$ function from the $sklearn.neighbors$ module implements learning based on the $k$ nearest neighbors of each query point, where $k$ is an integer value specified by the user. The $k$-neighbors classification in KNeighborsClassifier is the most commonly used technique. Since the optimal value $k$ is dependent on data we ran the experiment with multiple values of $k$ and found that the $k$=3 produces the best accuracy. In general a larger $k$ suppresses the effects of noise, but makes the classification boundaries less distinct.
 We used Euclidean distance as the distance metric and assigned equal weights to all the query points. In some cases it might be better to assign weights based on the distance. The close query point contribute more to the fit and the ones far contribute less. For our case the uniform weight with simple majority vote of the nearest neighbors worked just fine.

\subsection{SVM}
Our support vector machine algorithm was also implemented using scikit-learn. The $sklearn.svm.SVC$ class is based on libsvm and is capable of performing multi-class classification. Internally, they use libsvm and liblinear to handle all computations. These libraries are wrapped using C and Cython. It supports multi-class classification on a one-vs-one scheme. In this scheme a classifier is created for each pair of classes and during prediction, the class which receives most votes is assigned to the data point. In an event of a tie, the class with highest total confidence calculated by summing over the pair-wise classification confidence is selected. 
As the other classifiers, $skleran.SVM$ also takes as input two arrays: an array of training samples and another array of class labels. The training samples and labels are first sent to $fit$ function which fits the SVM model according to the data. The resulting model is then used to predict the labels of test data.

\section{Dataset}\label{dataset}
To have a variety of dataset we selected the following three datasets for our experiment.
Many experiments are data dependent. To see if our technique is not data dependent we used three different datasets.
\subsection{MNIST Dataset}
The MNIST database of handwritten digits maintained by Yann LeCun \cite{MNIST}, has a training set of 55,000 examples, and a test set of 10,000 examples. It is a subset of a larger set available from NIST. The digits have been size-normalized and centered in a fixed-size image. It is a good database for people who want to try learning techniques and pattern recognition methods on real-world data while spending minimal efforts on preprocessing and formatting. The MNIST database was constructed from NIST's Special Database 3 and Special Database 1 which contain binary images of handwritten digits. The original black and white (bilevel) images from NIST were size normalized to fit in a 20x20 pixel box while preserving their aspect ratio. The images were centered in a 28x28 image by computing the center of mass of the pixels, and translating the image so as to position this point at the center of the 28x28 field.

@@

\begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/digit.png}
            \caption{Sample EMNIST-MNIST dataset}
            \label{fig:EMNIST MNIST dataset}
        \end{subfigure}%
        \label{fig:Rotate-misclassifications}
        \begin{subfigure}[b]{\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/letter.png}
            \caption{Sample EMNIST-Letter dataset}
            \label{fig:EMNIST MNIST dataset}
        \end{subfigure}%
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Fashion MNIST Dataset}
Fashion-MNIST is a dataset of Zalando's article images-consisting of a training set of 55,000 examples and a test set of 10,000 examples. Each example is a 28x28 grayscale image, associated with a label from 10 classes.

### 2020-04-13 chapters/methodology/properties.tex
final draft

\section{Identifying Metamorphic Relations} 
We identified five metamorphic properties for each dataset used: rotation, shearing, shading, shifting along x-axis, and, shifting along y-axis. Each image in the testing dataset (digit, letter, and, fashion) was transformed using the five metamorphic properties. We used Keras image preprocessing functions to apply these transformations to the test data in each dataset to generate new data to measure robustness.
\subsection{Rotate}
The test images from each dataset is transformed The rotation transformation algorithm takes in an image and an angle in degrees as parameter and rotates the image with the given angle. For each angle in [\ang{-50}, \ang{50}] we transformed each image Each image (digit, letter, and, fashion) is rotated clockwise and counter clockwise between angles [\ang{-50}, \ang{50}]. 
    \begin{figure}[!htbp]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/rotate1.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/rotate2.png}
            \caption{Angle: \ang{0}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/rotate3.png}
            \caption{Angle: \ang{50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}
        \caption{Rotation property applied to Digit 3.}
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Shear}  
The images were transformed between angle [-50, 50]
    \begin{figure}[!htbp]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\linewidth]{images/shear1.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\textwidth]{images/shear2.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\linewidth]{images/shear3.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

@@

\subsection{Shading}
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shade1.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shade2.png}
            \caption{Value: 80}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shade3.png}
            \caption{Value: 99}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

@@

\subsection{Shifting in the X direction}
    For any value above x the image was completely out of the frame.
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shiftx1.png}
            \caption{Value: -10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shiftx2.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shiftx3.png}
            \caption{Value: 10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

@@

\subsection{Shifting in the Y direction}
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shifty1.png}
            \caption{Value: -10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shifty2.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shifty3.png}
            \caption{Value: 10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

@@

>>>>

\section{Identifying Metamorphic Relations} \label{identifyingMR}
We identified five metamorphic properties for each dataset: rotation, shearing, shading, shifting the image along x-axis, and, shifting the image along y-axis. Each image in the testing dataset (digit, letter, and, fashion) was transformed using the five metamorphic properties. We used Keras image preprocessing functions to apply these transformations to the test data in each dataset to generate new data to measure robustness.

There are 10000 test images in the in the MNIST digit dataset. There are 10 class labels from 0 to 9, and each class label has 1000 instances. We applied the following metamorphic properties to each test image.
\subsection{Rotate}
Since we are dealing with image datasets, we hypothesize that small changes to the images by rotating them clock-wise or counter clock wise would not have drastic effect on the accuracy of model. To test our hypothesis we rotated the test data at each angle between [\ang{-50}, \ang{50}]. We also expect certain digits with symmetry (like 0) will be less afftected by these metamorphic properties.
 Each image in the test dataset was transformed using keras ImageDataGenerator method. 
The test images from each dataset is transformed The rotation transformation algorithm takes in an image and an angle in degrees as parameter and rotates the image with the given angle. For each angle in [\ang{-50}, \ang{50}] we transformed each image Each image (digit, letter, and, fashion) is rotated clockwise and counter clockwise between angles [\ang{-50}, \ang{50}]. 
    \begin{figure}[!htbp]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/rotate1.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/rotate2.png}
            \caption{Angle: \ang{0}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/rotate3.png}
            \caption{Angle: \ang{50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}
        \caption{Rotation property applied to Digit 3.}
        \label{fig:Rotate-misclassifications}
    \end{figure}
    \FloatBarrier

\subsection{Shear} 
To shear the images we used image pre-processing library offered by Keras. The ImageDataGenerator class generates batches of tensor image data with real-time data augmentation. We used the ImageDataGenerator's $apply\_transform()$ method to apply a transformation to an image according to given parameters. The $apply\_transform()$ method takes in the image, transformation type, and, the amount of transformation to be applied as parameter. It then applies the transformation and returns a transformed version of the input in the same shape.
The transformation parameter we used here was $shear$ and the images were transformed between angle $[-50, 50]$.

    \begin{figure}[!htbp]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\linewidth]{images/shear1.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\textwidth]{images/shear2.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \includegraphics[width=\linewidth]{images/shear3.png}
            \caption{Angle: \ang{-50}}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

@@

\subsection{Shading}
We represent the pixels of the MNIST images as floats between 0 and 1 where, 0 is white and 1 represents black. To apply the shading transformation we added values to the white pixels of the test data until they become black.
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shade1.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shade2.png}
            \caption{Value: 80}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shade3.png}
            \caption{Value: 99}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

@@

\subsection{Shifting in the X direction}
Since the images were 28 pixels wide, shifting the images by more than 28 pixels in either direction moved the images out of the frame completely. Thus, we transformed the test datasets by moving each image by pixels between 0 and 28 in both the X directions. We used ImageDataGenerator's $apply\_transform()$ function with $tx$ parameter to perform this transformation.
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shiftx1.png}
            \caption{Value: 10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shiftx2.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shiftx3.png}
            \caption{Value: -10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

@@

\subsection{Shifting in the Y direction(ShiftY)}
The last metamorphic property we identified was shifting the images on Y axis. We used ImageDataGenerator's $apply\_transform()$ function with $ty$ parameter to transform the test data. Since the images are 28x28 pixels we shifted the images by each pixel between 0 and 28 pixels in both direction. 
    \begin{figure}[htb!]
        \centering
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shifty1.png}
            \caption{Value: -10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\textwidth]{images/shifty2.png}
            \caption{Value: 0}
            \label{fig:Rotate-misclass0}
        \end{subfigure}%
        \begin{subfigure}[b]{.3\textwidth}
            \centering
            \includegraphics[width=\linewidth]{images/shifty3.png}
            \caption{Value: 10}
            \label{fig:Rotate-misclass0}
        \end{subfigure}

@@

After generating all the transformed versions of the datasets they were saved to be used as follow-up test cases for our machine-learning algorithms.

### 2020-04-13 chapters/results/results.tex
final draft

\section{Overall Accuracy}
\begin{figure}
  \includegraphics[width=\linewidth]{images/rotation}
  \caption{MR: Rotation.}
  \label{fig:rotation 1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/shade}
  \caption{MR: Shading.}
  \label{fig: Shading}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/sheer}
  \caption{MR: Sheering.}
  \label{fig: Sheer}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/shift}
  \caption{MR: Shifting.}
  \label{fig: Shift}
\end{figure}

\section{Digit-by Accuracy}
\begin{figure}
  \includegraphics[width=\linewidth]{images/rotation1}
  \caption{MR: Rotation.}
  \label{fig:rotation 1}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/shade1}
  \caption{MR: Shading.}
  \label{fig: Shading}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/sheer1}
  \caption{MR: Sheering.}
  \label{fig: Sheer}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/shift1}
  \caption{MR: Shifting.}
  \label{fig: Shift}
\end{figure}

>>>>

In this section we will discuss our findings after implementing the machine learning algorithms and the metamorphic properties.

Accuracy is defined as the number of correct predictions made by the model with respect to the total number of predictions made. To evaluate the accuracy of our machine learning models, we first trained the models on the training data. The MNIST, Fashion-MNIST, and, EMNIST training datasets have 55000, 55000, and, 119800 training data respectively. The training data consists of the images and their corresponding labels which are used as input to the algorithm in order to generate a model. Once we generated the trained models, we used the test data to calculate the accuracy of the models. The MNIST, Fashion-MNIST, and, EMNIST testing dataset have 10000, 10000, and, 20800 testing data respectively. The following graphs show the accuracy of the various models on the test dataset.

\pgfplotstableread[row sep=\\,col sep=&]{
    interval & MNIST & Fashion & EMNIST \\
    CNN     & 97.01 & 83.56 & 78.20 \\
    NN     & 91.41 & 79.89 & 64.96 \\
    NB    & 80.85 & 65.6 & 57.81 \\
    KNN   & 97.28 & 85.24 & 86.25 \\
    SVM   & 95.47 & 84.56 & 81.25\\
    }\accuracy

\begin{center}
\begin{tikzpicture}
    \begin{axis}[
            ybar,
            bar width=.75cm,
            height=.5\textwidth,
            width=\textwidth,
            legend style={at={(0.5,1)},
                anchor=north,legend columns=-1},
            symbolic x coords={CNN,NN,NB,KNN, SVM},
            xtick=data,
            ytick={0,20,40,60,80,100},
            nodes near coords,
            nodes near coords align={vertical},
            ymin=0,ymax=120,
            ylabel={Accuracy},
            xlabel={Algorithms}
        ]
        \addplot table[x=interval,y=MNIST]{\accuracy};
        \addplot table[x=interval,y=Fashion]{\accuracy};
        \addplot table[x=interval,y=EMNIST]{\accuracy};
        \legend{MNIST, Fashion, EMNIST}
    \end{axis}
\end{tikzpicture}      
\end{center}{}
An interesting observation from the table above is that, deep learning algorithms are not necessarily always a good choice when we are trying to maximize accuracy. Depending on the type of dataset, regular machine learning algorithms like KNN can also yield high accuracy and outperform deep learning algorithms.
In the following sections we will discuss how the metamorphic transformations affected the accuracy of the models and what conclusions we can draw from it.
\section{Effect of metamorphic transformation on the accuracy of the model}
From literature review we saw that metamorphic testing can be a very useful technique to test the correctness of an algorithm. In this thesis, we will investigate the effect of the identified metamorphic properties on the accuracy of the machine learning algorithms. For each metamorphic property identified in \ref{identifyingMR} we want to see how the accuracy of the models change with the varying degree of transformation. Our hypothesis is that small changes to the input image should not affect the prediction of the model drastically. After creating a trained model with the training dataset, we applied the metamorphic properties on the training data to generate transformed versions of the test data. We calculated the following metrics to evaluate the effect of the metamorphic relations on machine learning algorithm. To tackle the stochastic nature of training a neural network model, we ran each of the above experiment ten times and calculated average for accuracy.

\input{figures.tex}

\clearpage
\subsection{Robustness}

In the section \ref{Digit-by Accuracy} we saw that that the accuracy of the algorithms varied depending upon the transformation applied to the test data as well as the degree of the transformation. Robustness is the property of an algorithm whereby if the test data is "similar" to the training data then the testing error is also close to the training error \cite{Xu2012}. Thus, a robust algorithm should produce similar errors while predicting similar test data. In this section, we will be comparing the robustness of the five algorithms with respect to each other for different metamorphic relations and verify the accuracy of the recommendations we made in the table \ref{tbl:indexrecommendations}. For this we generated a new dataset with those recommendations and compared it's accuracy with the accuracy of the original dataset. To generate a balanced dataset of 5000 samples we randomly picked 100 transformed images from each transformation for every class label. This new test dataset was then tested for accuracy on the five algorithms we implemented. The bar graph below shows the accuracy of the new test dataset as compared to the original MNIST dataset.

\pgfplotstableread[row sep=\\,col sep=&]{
    Algorithm & MNIST & Transformed  \\
    CNN     & 97.01 & 95.2 \\
    NN     & 91.41 & 89.02 \\
    NB    & 80.85 & 78.76 \\
    SVM   & 95.47 & 90.98\\
    KNN   & 97.28 & 93.06\\
    }\Robustness

\begin{figure}[H]
\begin{tikzpicture}
    \begin{axis}[
            ybar,
            bar width=.75cm,
            height=.5\textwidth,
            width=\textwidth,
            legend style={at={(0.5,1)},
                anchor=north,legend columns=-1},
            symbolic x coords={CNN,NN,NB,KNN, SVM},
            xtick=data,
            ytick={0,20,40,60,80,100},
            nodes near coords,
            nodes near coords align={vertical},
            ymin=0,ymax=120,
            ylabel={Accuracy},
            xlabel={Algorithms}
        ]
        \addplot table[x=Algorithm,y=MNIST]{\Robustness};
        \addplot table[x=Algorithm,y=Transformed]{\Robustness};
        \legend{MNIST, Transformed Images}
    \end{axis}
\end{tikzpicture}      
\caption{Accuracy of tranformed dataset vs original dataset}
\label{img:transformedaccuracy}
\end{figure}

The more robust algorithm will have the accuracy of the transformed images closer to the accuracy of the original MNIST data. From the graph above we see that the convolutional neural network has a $1.81\%$ decrease in accuracy while the accuracy of the neural-network, NB, KNN, and, SVM decreased by $2.39\%$, $2.09\%$, $4.22\%$, and, $4.49\%$ respectively. Thus, among the algorithms we implemented the convolutional neural network is proven to be the most robust followed by Naive Bayes implementation. While the KNN and SVM implementations are the least robust.

In Section \ref{4.1.1} we discovered that the accuracy of the test data decreased as the degree of the transformation was increased. So a second way of looking at robustness is to look at transformations which can be applied to the dataset without lowering the accuracy of the model below 90 percent of the original value.

\import{chapters/results/}{tables.tex}

\newpage
\section{Discussion}
In this paper we identified five metamorphic properties "Rotation", "Shading", "Shearing", "Shifting the image along $x$ axis", and, "Shifting the image along $y$ axis" that can be used with image datasets. We then applied these metamorphic transformations to three datasets: MNIST, Fashion-MNIST, and, EMNIST. We also looked at how the accuracy of the datasets are affected by the transformations we identified. We also investigated the accuracy of transformations on individual classes in the MNIST dataset. We then provide recommendations for creating follow up test cases from the MNIST dataset by using the minimum and maximum values of transformations to use for these metamorphic properties. We also implemented five common machine learning algorithms and evaluated their robustness on these metamorphic properties.
We make following recommendations for transforming digits in MNIST dataset.
This paper also make the following contributions: 
We made a methodological contribution where we have provided a set of functions to easily manipulate, and, transform image datasets for future research. Future researchers can utilize these functions to plugin more algorithms and metamorphic properties.

Contributions:
Methodological contribution where others can plugin more algors or MT.
Experimental contribution:Which algo does better.

Conclusions:

Framework to apply MT in midst of distortions.
CNN not so much better than others based on learning just from the dataset.
